### 2021-03-12 text/text.tex
refactor latex

Even though Edoc is a public server, its database does not have a
web-ready API. In addition, since Edoc is a production server, its
underlying database cannot be used directly on pain of disturbing the
provided services. The data hence needs to be extracted from Edoc in
order to work with it. This could for example be achieved by cloning the
database of the server and running it on a local machine. However, this
route was not available due to the limited resources of the responsible
co-workers. I thus employed a workaround: Edoc has a built-in advanced
search tool where the results can be exported. Even though it is not
possible to extract all database items by default, only one of the many
available search fields has to be filled in. The complete database can
hence be extracted by only filling in the \texttt{date} field and using
a sufficiently permissive time period such as 1940 to 2020 since the
oldest record in the database was published in 1942. On January 21 2021,
this query yielded 68'345 results. These results were then exported as a
326 MB JSON file called \texttt{1942-2020.json}. \texttt{1942-2020.json}
has two drawbacks. First, the maximum file size on GitHub is 100 MB. And
second, \texttt{1942-2020.json} is too big to be handled by standard
editors requiring special editors such as Oxygen. For these reasons
\texttt{1942-2020.json} was split into smaller files that are easier
handled and can be uploaded to GitHub. For this
\texttt{Utility.split\_json} was used yielding 14 files of size 20 MB or
less containing 5000 or fewer entries each. These files are called
\texttt{raw\_master\_\{year\}.json} and saved under
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.

@@

Each Edoc item has 43 main data fields. Most of these data fields belong
to the class of descriptive metadata. The data entry for an item's
descriptive metadata is undertaken by the person who uploads the item
which is in most cases one of the item's authors. The Note that an item
is first uploaded to the University of Basel's research database
\url{https://www.forschdb2.unibas.ch} before being automatically fed
into Edoc. There are explicit rules on how to enter the data as
summarized in the user manual (Universität Basel, n.d.). However, there
is no (or at least no systematic) manual or automatic validation of the
entered data. This means that some data fields are very heterogenous and
require further parsing (see \protect\hyperlink{gold-standard}{section
``Gold standard''}). The data fields that are of interest to the project
at hand are discussed in more detail in (see
\protect\hyperlink{sample-data-set}{section ``Sample data set''} below).

@@

There are a number of constraints for selecting the sample data set
pertaining to an items's text, evaluability and the data set's scope.

The first constraint stems from Annif, the machine indexing framework
that will be used. Put simply, machine indexing assigns index terms to a
text based on training data. The training data consists of a set of
texts, a vocabulary, and function from vocabulary to texts. In this
context we mean by ``text'' a sequence of words in a natural language
and by ``vocabulary'' a set of words. Intuitively, the training data
consists of pairs of text and subject terms that meet some standard. The
training data and the vocabulary are already supplied by Annif, we only
need to provide a text for each item that we want to be assigned index
terms. Therefore, we only select items with text.

@@

Taking into account the third constraint simply means that we do not
employ any further restrictions. We can hence construct the sample data
set by choosing exactly those items from
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}
which have non-empty data fields \texttt{title}, \texttt{abstract},
\texttt{id\_number}, and \texttt{keywords}. We do so by calling
\texttt{Data.select\_from\_file} iteratively for all files in
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.
The resulting file is saved in
\href{https://github.com/MHindermann/mas/tree/main/files/sample}{\texttt{/sample/}}
as \texttt{sample\_master.json}.

@@

Of the 68'345 items in
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}},
all have a title (non-empty \texttt{title} data field), a little more
than half of the items have an abstract (37'381 items with non-empty
\texttt{abstract} data field), roughly half of the items have an ID
(35'355 items with non-empty \texttt{id\_number} data field),\footnote{Note
  that when using the facet by blank on \texttt{id\_number} in
  OpenRefine, there are 57'153 matches; this is due to the fact that
  many items with an ID such as DOI have secondary or tertiary IDs such
  as ISI or PMID.} and less than 10\% of the items have keywords (6'660
items with non-empty \texttt{keywords} data field). The sample data set
as requires all the above data fields to be non-empty;
\texttt{/sample/sample\_master.json} has 4'111 items and hence
constitutes 6\% of the raw data.

@@

Annif (Suominen et al. 2021) is an open source multi-algorithm automated
indexing tool developed at the Finnish National Library (see Suominen
2019 for an overview). Training a local Annif instance for machine
indexing is currently evaluated at different libraries, for example at
the German National Library (Nagelschmidt 12.11.2020). As stated in
section \protect\hyperlink{introduction}{section ``Introduction''}, in
this project I am interested in using Annif out of the box. This means
that instead of training a local Annif instance, I will be relying on
the Annif REST-style API (see \url{https://api.annif.org/}).\footnote{This
  API is specifically intended for testing. For integration into a
  production system, the Finto AI API is available (see
  \url{https://ai.finto.fi/v1/ui/}).} The advantage of this approach is
that it is quick and relatively easy to implement. The disadvantage is
that no custom algorithms or vocabularies can be used. The task of
constructing a gold standard (see
\protect\hyperlink{gold-standard}{section ``Gold standard''}) remains
the same.

The vocabularies provided by the Annif API are the General Finnish
Ontology or YSO in short (see \url{https://finto.fi/yso/en/}) and
Wikidata (see \url{https://www.wikidata.org/}). Each vocabulary is
combined with an algorithm or algorithm ensemble respectively and a
specific language to create a so-called Annif ``project.'' The five
projects used in what follows are summarized in Table 1. A high-level
description of the algorithm(s) is given by Suominen (2019, 7--10).
Information on implementation can be found at the Annif GitHub Wiki (see
\url{https://github.com/NatLibFi/Annif/wiki}).

@@

In this section I will construct a derivative gold standard in order to
assess the quality of machine indexing the sample data set with Annif.

@@

In a first step, the keywords must be extracted from the sample data set
\texttt{/sample/sample\_master.json}. Recall that we mandated a
non-empty \texttt{keywords} data field for an item to be selected from
the raw Edoc data (see \protect\hyperlink{selection}{subsection
``Selection''}). We can thus simply copy the information in the
\texttt{keywords} data field on a per item basis. To do this, we call
\texttt{Keywords.extract\_keywords} with the sample data set as argument
and save the output as \texttt{keywords/keywords\_extracted.json} like
so:

@@

In second step, a list of all single keywords must be created. In order
to do so, let us consider now in more detail the exact information
extracted from the \texttt{keywords} data fields as per
\texttt{/keywords/keywords\_extracted.json}. In Edoc, the
\texttt{keywords} data field of an item is a non-mandatory free text
field that is filled in by the user (usually one of the authors) who
undertakes the data entry of an item to Edoc. Even though the Edoc user
manual specifies that keywords must be separated by commas (Universität
Basel, n.d., 8), this requirement is neither validated by the input mask
nor by an administrator of Edoc. Furthermore, neither the manual nor the
input mask provide a definition of the term ``keyword.'' A vocabulary or
a list of vocabularies from which to choose the keywords is also
lacking. Taken together, these observations are indicative of very
heterogeneous data in the \texttt{keywords} data field. To wit, the
items of \texttt{/keywords/keywords\_extracted.json} are strings where
single keywords are individuated by any symbols the user saw fit. So,
for each item in \texttt{/keywords/keywords\_extracted.json}, the user
input must be parsed into single keywords.

Next the so parsed single keywords must be cleaned or normalized: we
want the keywords to follow a uniform format thereby joining
morphological duplicates such as ``Gene,'' ``gene,'' ``gene\_,''
``gene/,'' and so on. Also, some keywords are in fact keyword chains,
for example ``Dendrites/metabolism/ultrastructure.'' Keyword chains must
be broken into their component keywords and then parsed again. The
reason for this is that Annif only assigns flat keywords and not keyword
chains.

@@

The median number of keywords for an item in the sample data set is 6
with an IQR of 4 (min = 0, Q1 = 4, M = 6, Q3 = 8, max = 87). Of course,
items in the sample data set with a number of keywords below the first
and above the third quartile are highly suspect from a qualitative point
of view: when it comes to subject indexing, some terms are required, but
more is usually worse. Items with too few or too many keywords will be
discussed in more detail in section
\protect\hyperlink{assessment}{section ``Assessment''}

@@

With these improvements in place, each keyword with a suggestion was
assigned a QID via the ``Add cloumns from reconciled values''-function
(and similar for YSO and MeSH identifiers). The data was then exported
and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
a QID now constitute 69\% of all keywords and 78\% of their total
occurrences in the sample data set, but these numbers are significantly
lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
of all occurrences) and especially low for the YSO identifier (26.9\% of
all keywords with 11\% of all occurrences). In both cases, the problem
is due to the fact that Wikidata's mapping of MeSH respectively YSO is
only partial. There can be two reasons for this state of affairs for a
given entry: either there is no match between Wikidata and YSO or MeSH
(after all, Wikidata is much larger than MeSH and YSO taken together),
or there is a match but it has not yet been added to the mapping. In the
latter case, at least with respect to YSO, there is a solution: Finto
provides a REST-style API to access the YSO vocabulary directly (see
\url{https://api.finto.fi/}). For each keyword in the list of reference
keywords that lacks a YSO identifier, the Finto API is queried; if a
term turns up, it is added to the keyword. The effect of this second
reconcilement is detailed in Figure 4. It is achieved by calling
\texttt{Keywords.enrich\_with\_yso} on
\texttt{/keywords/keywords\_reference.json} and saving the output as
\texttt{/keywords/keywords\_reference\_master.json}

@@

Finally, consider the distribution of the cleaned and reconciled
keywords per item in the Edoc sample data set. The corresponding data is
generated with \texttt{Keywords.make\_count} as described in
\protect\hyperlink{analysis}{subsection Analysis} above and available as
\texttt{/analysis/keywords\_counted.json}. Figure 5 shows that the
median number of keywords from MeSH or YSO might be too low to be
adequate. This problem can be amended by imposing further constraints on
the sample data set and such a solution is discussed in section {[}!!
section{]}.

@@

The metrics used for the assessment are precision, recall and F1-score.
Precision and recall are standard metrics for indexing quality (e.g.,
Gantert 2016, 197) whereby the F1 score plays are more prominent role in
the assessment of machine indexing (e.g., Suominen 2019, 11--14; Toepfer
and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
(such as indexing consistency, transparency, reproducibility) that are
neglected here.

@@

The above scoring metrics were implemented using the scikit-learn
machine learning library (Pedregosa et al. 2011).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Annif project (algorithm plus vocabulary) responsible for the
  indexing of the sample data set. As per the Annif REST API, these are
  \texttt{yso-en}, \texttt{yso-maui-en}, \texttt{yso-bonsai-en},
  \texttt{yso-fasttext-en}, and \texttt{wikidata-en}.
\item
  The text base per item, namely title versus title and abstract.
\item
  The maximum number of suggestions per item. Since we required 10
  suggestions per item, we can choose between 1-10 suggestions.
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_all_project+abstract.pdf}
\caption{Distribution of weighted F1-scores per class of project of
Annif configuration (left) and per class of text basis of Annif
configuration (right). \texttt{wikidata} (min = 0.239, Q1 = 0.355, M =
0.415, Q3 = 0.492, max = 0.517) outperforms any YSO configuration.
\texttt{yso-bonsai-en}, \texttt{yso-en} and \texttt{yso-fasttext-en} are
on par (min = 0.169, Q1 = 0.218, M = 0.312, Q3 = 0.414, max = 0.496) and
slightly outperformed by the more consistent \texttt{yso-maui-en} (min =
0.171, Q1 = 0.250, M = 0.327, Q3 = 0.407, max = 0.496). Surprisingly,
the performance of configurations based on titles (min = 0.169, Q1 =
0.250, M = 0.345, Q3 = 0.424, max = 0.517) was marginally better than
the performance of configurations based on titles and abstracts (min =
0.169, Q1 = 0.242, M = 0.337, Q3 = 0.424, max = 0.517).}
\end{figure}

@@

Let us turn to the parameter of the maximum number of suggestions per
item in the Edoc sample data set (see Figure 8). Here the best
performance was achieved by a token n = 4 configuration. However, the
type n = 4 configuration performed on average significantly worse than
the type n = 3 and type n = 2 configurations. So with respect to the
maximum number of suggestions, there is a discrepancy between the best
performing token configuration and the best performing type of
configuration. This distinction is important: when choosing a
configuration for the purpose of a production system, we are usually
interested in the best token configuration. The top 20 token
configurations are summarized in Figure 9. The best performing
configuration with a weighted F1-score of 0.517 is \texttt{wikidata-en}
with a maximum number of 4 suggestions per item; the text basis (title
or abstract and title) does not matter.

@@

Let us now look at the results. First consider the distribution of the
performance scores across departments as shown in Figure 11. We can see
that there are striking differences in variability between departments.
The departments with the most consistent weighted F1-scores are Medicine
and Central Services. However, these two departments have also the
lowest maximum weighted F1-scores. It is noteworthy that all other
departments have maximum weighted F1-scores that are well above the
weighted F1-score of 0.517 of the best performing general Annif
configuration.

@@

Let us now consider the best performing Annif configurations per
department as summarized in Figure 12. It is evident that only two of
the ten departments (namely Associated and Central Services) have as
best performing configuration the configuration that was declared the
overall best performing configuration (namely
\texttt{wikidata-en-F-F-4-N}). More surprisingly, YSO outperforms
Wikidata in all other departments except Interdisciplinary. However, the
margin is rather slim. The notable exception is the department
Economics, where the YSO configuration outperforms the Wikidata
configuration by a factor of 3. More importantly, the best performing
YSO configurations are significantly less productive than the slightly
worse performing Wikidata configuration, except for
\texttt{yso-en-F-F-4-N} in the Medicine department.

>>>>

Even though Edoc is a public server, its database does not have a
web-ready API. In addition, since Edoc is a production server, its
underlying database cannot be used directly on pain of disturbing the
provided services. The data hence needs to be extracted from Edoc in
order to work with it. This could for example be achieved by cloning the
database of the server and running it on a local machine. However, this
route was not available due to the limited resources of the responsible
co-workers. I thus employed a workaround: Edoc has a built-in advanced
search tool where the results can be exported. Even though it is not
possible to extract all database items by default, only one of the many
available search fields has to be filled in. The complete database can
hence be extracted by only filling in the \texttt{date} field and using
a sufficiently permissive time period such as 1940 to 2020 since the
oldest record in the database was published in 1942. On January 21 2021,
this query yielded 68'345 results. These results were then exported as a
326 MB JSON file called \texttt{1942-2020.json}. \texttt{1942-2020.json}
has two drawbacks. First, the maximum file size on GitHub is 100 MB. And
second, \texttt{1942-2020.json} is too big to be handled by standard
editors requiring special editors. For these reasons
\texttt{1942-2020.json} was split into smaller files that are easier
handled and can be uploaded to GitHub. For this
\texttt{Utility.split\_json} was used yielding 14 files of size 20 MB or
less containing 5000 or fewer entries each. These files are called
\texttt{raw\_master\_\{year\}.json} and saved under
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.

@@

Each Edoc item has 43 main data fields. Most of these data fields belong
to the class of descriptive metadata. The data entry for an item's
descriptive metadata is undertaken by the person who uploads the item
which is (in most cases) one of the item's authors. Note that an item is
first uploaded to the University of Basel's research database
\url{https://www.forschdb2.unibas.ch} before being automatically fed
into Edoc. There are explicit rules on how to enter the data as
summarized in the user manual (Universität Basel, n.d.). However, there
is no (or at least no systematic) manual or automatic validation of the
entered data. This means that some data fields are very heterogenous and
require further parsing (see \protect\hyperlink{gold-standard}{section
``Gold standard''}). The data fields that are of interest to the project
at hand are discussed in more detail in (see
\protect\hyperlink{sample-data-set}{section ``Sample data set''} below).

@@

There are a number of constraints for selecting the sample data set
pertaining to an items's text, evaluability, and the data set's scope.

The first constraint stems from Annif, the machine indexing framework
that will be used (see \protect\hyperlink{machine-indexing}{section
``Machine indexing''} for more details). Put simply, machine indexing
assigns index terms to a text based on training data. The training data
consists of a set of texts, a vocabulary, and function from vocabulary
to texts. In this context we mean by ``text'' a sequence of words in a
natural language and by ``vocabulary'' a set of words. Intuitively, the
training data consists of pairs of text and subject terms that meet some
standard. The training data and the vocabulary are already supplied by
Annif, we only need to provide a text for each item that we want to be
assigned index terms. Therefore, we only select items with text.

@@

Taking into account the third constraint simply means that we do not
employ any further restrictions. We can hence construct the Edoc sample
data set by choosing exactly those items from
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}
which have non-empty data fields \texttt{title}, \texttt{abstract},
\texttt{id\_number}, and \texttt{keywords}. We do so by calling
\texttt{Data.select\_from\_file} iteratively for all files in
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}}.
The resulting file is saved in
\href{https://github.com/MHindermann/mas/tree/main/files/sample}{\texttt{/sample/}}
as \texttt{sample\_master.json}.

@@

Of the 68'345 items in
\href{https://github.com/MHindermann/mas/tree/main/files/raw}{\texttt{/raw/}},
all have a title (non-empty \texttt{title} data field), a little more
than half of the items have an abstract (37'381 items with non-empty
\texttt{abstract} data field), roughly half of the items have an ID
(35'355 items with non-empty \texttt{id\_number} data field),\footnote{Note
  that when using the facet by blank on \texttt{id\_number} in
  OpenRefine, there are 57'153 matches; this is due to the fact that
  many items with an ID such as DOI have secondary or tertiary IDs such
  as ISI or PMID.} and less than 10\% of the items have keywords (6'660
items with non-empty \texttt{keywords} data field). The Edoc sample data
set as requires all the above data fields to be non-empty;
\texttt{/sample/sample\_master.json} has 4'111 items and hence
constitutes 6\% of the raw data.

@@

Annif (Suominen et al. 2021) is an open source multi-algorithm automated
indexing tool developed at the Finnish National Library (see Suominen
2019 for an overview). Training a local Annif instance for machine
indexing is currently evaluated at different libraries, for example at
the German National Library (see Nagelschmidt 12.11.2020). As stated in
section \protect\hyperlink{introduction}{section ``Introduction''}, in
this project I am interested in using Annif out of the box. This means
that instead of training a local Annif instance, I will be relying on
the Annif REST-style API (see \url{https://api.annif.org/}).\footnote{This
  API is specifically intended for testing. For integration into a
  production system, the Finto AI API is available (see
  \url{https://ai.finto.fi/v1/ui/}).} The advantage of this approach is
that it is quick and relatively easy to implement. The disadvantage is
that no custom algorithms or vocabularies can be used. The task of
constructing a gold standard (see
\protect\hyperlink{gold-standard}{section ``Gold standard''}) remains
the same.

The vocabularies provided by the Annif API are the General Finnish
Ontology or YSO in short (see \url{https://finto.fi/yso/en/}) and
Wikidata (see \url{https://www.wikidata.org/}). Each vocabulary is
combined with an algorithm or algorithm ensemble respectively and a
specific language to create a so-called Annif ``project.'' The five
projects used in what follows are summarized in Table 1. A high-level
description of the algorithm(s) is given by Suominen (2019, 7--10).
Information on the implementation of the algorithm(s) can be found at
the Annif GitHub Wiki (see
\url{https://github.com/NatLibFi/Annif/wiki}).

@@

In this section I will construct a derivative gold standard in order to
assess the quality of machine indexing the Edoc sample data set with
Annif.

@@

In a first step, the keywords must be extracted from the Edoc sample
data set \texttt{/sample/sample\_master.json}. Recall that we mandated a
non-empty \texttt{keywords} data field for an item to be selected from
the raw Edoc data (see \protect\hyperlink{selection}{subsection
``Selection''}). We can thus simply copy the information in the
\texttt{keywords} data field on a per item basis. To do this, we call
\texttt{Keywords.extract\_keywords} with the sample data set as argument
and save the output as \texttt{keywords/keywords\_extracted.json} like
so:

@@

In a second step, a list of all single keywords must be created. In
order to do so, let us consider now in more detail the exact information
extracted from the \texttt{keywords} data fields as per
\texttt{/keywords/keywords\_extracted.json}. In Edoc, the
\texttt{keywords} data field of an item is a non-mandatory free text
field that is filled in by the user (usually one of the authors) who
undertakes the data entry of an item to Edoc. Even though the Edoc user
manual specifies that keywords must be separated by commas (Universität
Basel, n.d., 8), this requirement is neither validated by the input mask
nor by an administrator of Edoc. Furthermore, neither the manual nor the
input mask provide a definition of the term ``keyword.'' A vocabulary or
a list of vocabularies from which to choose the keywords is also
lacking. Taken together, these observations are indicative of very
heterogeneous data in the \texttt{keywords} data field. To wit, the
items of \texttt{/keywords/keywords\_extracted.json} are strings where
single keywords are individuated by any symbols the user saw fit. So,
for each item in \texttt{/keywords/keywords\_extracted.json}, the user
input must be parsed into single keywords.

Next the so parsed single keywords must be cleaned or normalized: we
want the keywords to follow a uniform format thereby joining
morphological duplicates such as ``Gene,'' ``gene,'' ``gene\_,''
``gene/,'' and so on. Also, some keywords are in fact keyword chains,
for example ``Dendrites/metabolism/ultrastructure.'' Keyword chains must
be broken into their component keywords and then parsed again. The
reason for this is that Annif only assigns flat (i.e., non-hierarchical)
keywords and not keyword chains.

@@

The median number of keywords for an item in the sample data set is 6
with an IQR of 4 (min = 0, Q1 = 4, M = 6, Q3 = 8, max = 87). Of course,
items in the sample data set with a number of keywords below the first
and above the third quartile are highly suspect from a qualitative point
of view: when it comes to subject indexing, some terms are required, but
more is usually not better but worse. Items with too few or too many
keywords will be discussed in more detail in section
\protect\hyperlink{assessment}{section ``Assessment''}

@@

With these improvements in place, each keyword with a suggestion was
assigned a QID via the ``Add cloumns from reconciled values''-function
(and similar for YSO and MeSH identifiers). The data was then exported
and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
a QID now constitute 69\% of all keywords and 78\% of their total
occurrences in the sample data set, but these numbers are significantly
lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
of all occurrences) and especially low for the YSO identifier (26.9\% of
all keywords with 11\% of all occurrences). In both cases, the problem
is due to the fact that Wikidata's mapping of MeSH respectively YSO is
only partial. There can be two reasons for this state of affairs for a
given entry: either there is no match between Wikidata and YSO or MeSH
(after all, Wikidata is much larger than MeSH and YSO taken together),
or there is a match but it has not yet been added to the mapping. In the
latter case, at least with respect to YSO, there is a solution: Finto
provides a REST-style API to access the YSO vocabulary directly (see
\url{https://api.finto.fi/}). For each keyword in the list of reference
keywords that lacks a YSO identifier, the Finto API is queried; if a
term turns up, it is added to the keyword. The effect of this second
reconcilement is detailed in Figure 4. It is achieved by calling
\texttt{Keywords.enrich\_with\_yso} on
\texttt{/keywords/keywords\_reference.json} and saving the output as
\texttt{/keywords/keywords\_reference\_master.json} like so:

@@

Finally, consider the distribution of the cleaned and reconciled
keywords per item in the Edoc sample data set. The corresponding data is
generated with \texttt{Keywords.make\_count} as described in
\protect\hyperlink{analysis}{subsection Analysis} above and available as
\texttt{/analysis/keywords\_counted.json}. Figure 5 shows that the
median number of keywords from MeSH or YSO might be too low to be
adequate. This problem can be amended by imposing further constraints on
the Edoc sample data set and such a solution is discussed in
\protect\hyperlink{conclusion-and-outlook}{section ``Conclusion and
outlook''}.

@@

The metrics used for the assessment are precision, recall and F1-score.
Precision and recall are standard metrics for indexing quality (e.g.,
Gantert 2016, 197) whereby the F1-score plays are more prominent role in
the assessment of machine indexing (e.g., Suominen 2019, 11--14; Toepfer
and Kempf 2016, 93f.). Of course, there is a host of alternative metrics
(such as indexing consistency, transparency, reproducibility) that are
neglected here.

@@

The above scoring metrics were implemented using the scikit-learn Python
machine learning library (Pedregosa et al. 2011).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Annif project (algorithm plus vocabulary) responsible for the
  indexing of the sample data set. As per the Annif REST API, these are
  \texttt{yso-en}, \texttt{yso-maui-en}, \texttt{yso-bonsai-en},
  \texttt{yso-fasttext-en}, and \texttt{wikidata-en}.
\item
  The text base per item, namely title versus title and abstract.
\item
  The maximum number of suggestions per item. Since we required 10
  suggestions per item, we can choose between 1 to 10 suggestions.
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_all_project+abstract.pdf}
\caption{Distribution of weighted F1-scores per class of project of
Annif configuration (left), and per class of text basis of Annif
configuration (right). \texttt{wikidata-en} (min = 0.239, Q1 = 0.355, M
= 0.415, Q3 = 0.492, max = 0.517) outperforms any YSO configuration.
\texttt{yso-bonsai-en}, \texttt{yso-en} and \texttt{yso-fasttext-en} are
on par (min = 0.169, Q1 = 0.218, M = 0.312, Q3 = 0.414, max = 0.496) and
slightly outperformed by the more consistent \texttt{yso-maui-en} (min =
0.171, Q1 = 0.250, M = 0.327, Q3 = 0.407, max = 0.496). Surprisingly,
the performance of configurations based on titles (min = 0.169, Q1 =
0.250, M = 0.345, Q3 = 0.424, max = 0.517) was marginally better than
the performance of configurations based on titles and abstracts (min =
0.169, Q1 = 0.242, M = 0.337, Q3 = 0.424, max = 0.517).}
\end{figure}

@@

Let us turn to the parameter of the maximum number of suggestions per
item in the Edoc sample data set (see Figure 8). Here the best
performance was achieved by a token n = 4 configuration. However, the
type n = 4 configuration performed on average significantly worse than
the type n = 3 and type n = 2 configurations. So with respect to the
maximum number of suggestions, there is a discrepancy between the best
performing token configuration and the best performing type of
configuration. This distinction is important: when choosing a
configuration for the purpose of a production system, we are usually
interested in the best token configuration. The top 20 token
configurations are summarized in Figure 9. The best performing
configuration with a weighted F1-score of 0.517 is \texttt{wikidata-en}
with a maximum number of 4 suggestions per item; its text basis (title
or abstract and title) does not matter.

@@

Let us now look at the results. First consider the distribution of the
performance scores across departments as shown in Figure 10. We can see
that there are striking differences in variability between departments.
The departments with the most consistent weighted F1-scores are Medicine
and Central Services. However, these two departments have also the
lowest maximum weighted F1-scores. It is noteworthy that all other
departments have maximum weighted F1-scores that are well above the
weighted F1-score of 0.517 of the best performing general Annif
configuration.

@@

Let us now consider the best performing Annif configurations per
department as summarized in Figure 11. It is evident that only two of
the ten departments (namely Associated and Central Services) have as
best performing configuration the configuration that was declared the
overall best performing configuration (namely
\texttt{wikidata-en-F-F-4-N}). More surprisingly, YSO outperforms
Wikidata in all other departments except Interdisciplinary. However, the
margin is rather slim. The notable exception is the department
Economics, where the YSO configuration outperforms the Wikidata
configuration by a factor of 3. More importantly, the best performing
YSO configurations are significantly less productive than the slightly
worse performing Wikidata configuration, except for
\texttt{yso-en-F-F-4-N} in the Medicine department.
